Data Pre-Processing

### 2021-06-15 AST-Framing-Ontario/Data Pre-Processesing.rmd
June 15th
- Combined clean academic papers
- Sentiment analysis testing
- Bi-gram visualization update

---
title: "Data Pre-Processing"
author: "Jason Lam"
date: "11/03/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
params:
  Academic_Papers_SinglCol: "Texts/Academic Papers Trimmed Single Col"
  Academic_Papers_DoubCol: "Texts/Academic Papers Trimmed Double Col"
  Consortia: "Texts/Consortia"
  Municipalities_Regions: "Texts/Municipalities or Regions"
  School Boards: "Texts/School Boards"
  AP_stopW: !r c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
  Con_stopW: !r c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
  Mun_Reg_stopW: !r c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
  SB_stopW: !r c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")

@@

Load the following packages:
```{r}
library(dplyr)
library(ggraph)
library(ggplot2)
library(igraph)
library(pdftools)
library(readr)
library(reshape2)
library(stringr)
library(text2vec)
library(tidyr)
library(tidytext)
library(tm) 
library(tools)
library(topicmodels)
library(word2vec)
library(wordcloud)
```

@@

# Adjust the parameter below to filter out based on number of occurence
# Error will occur if n is outide the range of occurences 
bigram_graph <- bigram_counts %>%
  filter(n > 5) %>%
  graph_from_data_frame()

@@

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)

@@

>>>>

---
title: "Data Pre-Processing"
author: "Jason Lam"
date: "11/03/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
params:
  Academic_Papers_SinglCol: "Texts/Academic Papers Trimmed Single Col"
  Academic_Papers_DoubCol: "Texts/Academic Papers Trimmed Double Col"
  Consortia: "Texts/Consortia"
  Municipalities_Regions: "Texts/Municipalities or Regions"
  School Boards: "Texts/School Boards"
  AP_stopW: !r c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
  Con_stopW: !r c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
  Mun_Reg_stopW: !r c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", m  "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
  SB_stopW: !r c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")

@@

Load the following packages:
```{r}
library(dplyr)
library(ggraph)
library(ggplot2)
library(igraph)
library(pdftools)
library(readr)
library(reshape2)
library(stringr)
library(text2vec)
library(textdata)
library(tidyr)
library(tidytext)
library(tm) 
library(tools)
library(topicmodels)
library(word2vec)
library(wordcloud)
```

@@

a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

# Adjust the parameter below to filter out based on number of occurence
# Error will occur if n is outide the range of occurences

bigram_graph <- bigram_counts %>%
  filter(n > 100) %>%
  graph_from_data_frame()

@@

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point(color = "lightgreen", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()

@@

```{r}
bing <- get_sentiments(lexicon = "nrc")
colnames(vocab)[1] <- "word"
senti <- inner_join(bing, vocab, by= "word")
